---
title: 'Equotip hardness measurements - Tool function experiment'
author: "Lisa Schunk"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cerulean
    highlight: pygments
    number_sections: true
  github_document: 
    toc: true
    toc_depth: 3
    html_preview: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_format = "all", 
  knit_root_dir = rprojroot::find_rstudio_root_file()) })
---


```{r Knitr Options, include=FALSE}
knitr::opts_chunk$set(comment=NA, message=FALSE, indent="", error=TRUE)
````

---


# Goal of the script
This script reads the xlsx file (measurements have been generated with the Equotip Leeb C rebound)  and formats the data for a statistical analysis.  
The script will:

1. Read in the original xlsx file and organise the data 
2. Plot the data 
3. Write an XLSX-file and save an R object ready for further analysis in R 



```{r}
dir_in <- "analysis/raw_data_TFE/"
dir_out <- "analysis/plots"
```

Raw data must be located in `r paste0("~/", dir_in)`.  
Formatted data will be saved in `r paste0("~/", dir_out)`.
The knit directory for this script is the project directory.


---


# Load packages
```{r}
library(openxlsx)
library(tools)
library(readr)
library(ggplot2)
library(readxl)
library(tidyverse)
library(wesanderson)
```

---


# Get name, path and information of the file
```{r}
data_file <- list.files(dir_in, pattern = "\\.xlsx$", full.names = TRUE)
md5_in <- md5sum(data_file)
info_in <- data.frame(files = basename(names(md5_in)), checksum = md5_in, 
                      row.names = NULL)
```

The checksum (MD5 hashes) of the imported files are:  
```{r, echo = FALSE}
info_in
```



# Read in original xlsx-file
```{r}
imp_data <- read.xlsx(xlsxFile = data_file, sheet = 1, startRow = 3, colNames = TRUE, 
                      rowNames = FALSE, skipEmptyRows = FALSE) 

# changes the mode of 'hardness in HLC from character to numeric 
imp_data$hardness.in.HLC <- as.numeric(imp_data$hardness.in.HLC)
str(imp_data)

flint <- imp_data[1:11,]
lydite <- imp_data[15:52,]
balve <- imp_data[53,]

```



#### 4. Data analsysis - stats  

```{r}
# descriptive statistics 
# flint
length(flint[["ID"]])
summary(flint[["hardness.in.HLC"]])

# schist
length(lydite[["ID"]])
summary(lydite[["hardness.in.HLC"]])

# balve (MU-278)
length(balve[["ID"]])
summary(balve[["hardness.in.HLC"]])

```


# Data analsysis - plot 
```{r}
# boxplot
data_plot <- ggplot (imp_data, aes(y = hardness.in.HLC, x = raw.material, 
                                   fill = raw.material)) + 
  theme_classic() + 
  theme(legend.title = element_blank()) +
  geom_boxplot() + 
  scale_fill_manual(values=wes_palette(n =3,name = "Darjeeling2")) +
  geom_jitter() + labs(x="raw material", y="Leeb Rebound Hardness in HLC", title="") 

print(data_plot)

```



# Save data
## Define output file name
```{r}
file_out <- paste0(file_path_sans_ext(info_in[["file"]]), "_TFE_plot", ".pdf")
ggsave(filename = file_out, plot = data_plot, path = dir_out, device = "pdf")

```
The files will be saved as "`r paste0("~/", dir_out, ".[ext]")`".

---


# Show plot files information
```{r}
info_out <- list.files(path = dir_out, pattern = "\\.pdf$", 
                       full.names = TRUE) %>% 
            md5sum()
```


The checksum (MD5 hashes) of the exported files are:  
```{r, echo = FALSE}
info_out
```

---

# sessionInfo() and RStudio version
```{r}
sessionInfo()
```

---

RStudio version `r readLines("analysis/scripts/RStudioVersion.txt", n = 1)`.


--- 

END OF SCRIPT